---
title: "Darrell’s Machine Learning Notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Educational Media

* Introduction to Machine Learning (MIT OpenCourseWare) [youtube.com]<https://youtu.be/h0e2HAPTGF4>

```{r cars}
summary(cars)
```

## Key Modelling Point

### Five essential components of machine learning

1. What's the training data and how to evaulate the success of the system
2. How are we going to represent features of each instance in the model (height, weight, etc.)
3. How are we going to measure distances between the features (What's close?)
4. What's the best optimization 
5. What's the best cluster

#### Features
How do you build a matrix of features and weights

* Often a tradeoff between false negatives (*is a reptile* but isn't classified as one) and false positives (*isn't a reptile* but is classified as one)

How to you measure the distance between features and how to weigh relative importance

* Euclidian distance (square root of the sum of the distance)
* Manhattan difference ("one street at a time")

#### Clustering

* Cluster examples (observed training data)
* Make predictions (test data - unseen data)


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
