---
title: "Working with UserTests"
output:
  html_document:
    number_sections: yes
editor_options:
  chunk_output_type: inline
---

The functions in this package compute success rates and confidence intervals following [Jeff Sauro's excellent write up on MeasuringU](https://measuringu.com/wald/)

# Install packages
Install and load the ``UserTests`` package and some other packages.

```{r echo=TRUE}
#install.packages("readr", repos = "http://cran.us.r-project.org" )
library(readr)
#install.packages("devtools", repos = "http://cran.us.r-project.org")
library(devtools)
#devtools::install_github(repo = "darrellpenta/UserTests")
library(UserTests)
```

# Quick Analyses

If you just want to run analyses on a single task for which you know the success rate and the number of trials, provide that information to the ``UserTests::completion`` function, as below. 


```{r, echo=TRUE}
mydata <-
  UserTests::completion(.success=7, .trials=17)
mydata
```

The results returned indicate:

1. **successes**
The total number of success
1. **trials**  
The total number of trials
1. **orig.succ.pct**  
The raw success rate as a percentage
1. **estimator** 
The name of the method used to adjust the sucess rate (see [Lewis & Sauro, 2006](http://uxpajournal.org/wp-content/uploads/pdf/JUS_Lewis_May2006.pdf])).
1. **success.pct** 
The adjusted success rate as a percentage
1. **low.ci.pct**  
The lower confidence limit as a percentage
1. **hi.ci.pct**  
The upper confidence limit as a percentage

# Analyzing larger data sets

## Get your data in order
 
Start by properly preparing your data file, which should be saved in``.csv`` format. The data file should have either 3 or 4 columns, depending upon whether one or two test groups are being analyzed. 

In both cases, three of the columns should be: **Participant**, **Task**, and **Success**. The fourth (optional) column shuold be **Group**. See table 1:

Table 1

Participant | Task | Success | Group   
----------- | ---- | ------- | ----- 
 1          | 1    |  1      | US    
 1          | 1    |  0      | THEM      
 1          | 2    |  1      | US    
 1          | 2    |  1      | THEM     
 2          | 1    |  1      | US    
 2          | 1    |  0      | THEM      
 2          | 2    |  0      | US    
 2          | 2    |  1      | THEM
 ...        | ...  | ...     | ...


## Import the data
Next, import the file into R.

```{r}
mydata<-
  readr::read_csv("sample data/sample_data_2.csv")
head(mydata)
```


## Create a table of the adjusted completion rate means and confidence intervals
Run the completion function on your data set to view table of summarized data.
```{r}
mytable<-
  completion(mydata)
head(mytable)

```

## Export the table

You can export the table as a ``.csv`` file if you'd like one. Provide the path argument as in the example.
```{r eval=FALSE}
readr::write_csv(mytable, path = "..\MyDesktop\MyUsabilityStudy\completion-rates.csv")
```

# Create a figure
If you need a figure, use the ``comp_._figure`` function. You can overwrite the default labels by providing your own.

```{r}
myfigure <-
  comp_figure(mytable, xlabel="Test Task", ylabel = "Success (%)", legend_lab="Groups")
myfigure
```

# Saving the figure

To save the figure, provide the output format and path. The easiest way is to combine both of these in one string.  Acceptable file formats include:

* eps
* ps
* tex
* pdf
* jpeg
* tiff
* png
* bmp
* svg
* wmf

```{r eval=FALSE}
ggsave("../MyDesktop/usability-test-figure.png")
```

